Verifying Spatial Properties of Array Computations

### 2017-04-18 oopsla17/evaluation.tex
reworking eval a bit, adding back + histo

We measured the frequency at which individual specifications involved
multiple occurences of \term{*}
 % and \term{+}:
\begin{center}
\vspace{0.25em}
\setlength{\tabcolsep}{0.57em}
{\small{
\hspace{-1em}\begin{tabular}{c|cccccccc}
& 0 & 1 & 2 & 3 & 4 & 5 & 6  \\ \hline
\term{*} & \num{\overallmulOpszero} & \num{\overallmulOpsone} & \num{\overallmulOpstwo} & \num{\overallmulOpsthree} & \num{\overallmulOpsfour} & \num{0} & \num{\overallmulOpssix}
\end{tabular}}}
\vspace{0.2em}
\end{center}
\noindent
% \eg{}, roughly half the specifications did not involve $\term{*}$,
% a quarter use one $\term{*}$ and just under a quarter
% use two $\term{*}$ operators.

\paragraph{Limitations}

There were various reasons why we did not infer
specifications on every looped array computation: \\
\noindent
1) \textbf{Non-subset induction variables} occur when the
induction variables on the RHS are not a subset of those in the LHS. These
cases are not stencils by our definition. The degenerate case of this
is to have only constant indices on the LHS. We see lots of examples
of this in loops as accumulators \eg{} computing the sum over an array; \\
\noindent
2) \textbf{Derived induction variables} where an
index (\mintinline{fortran}{x}) is derived from an
induction variable (\mintinline{fortran}{i}) as in
\mintinline{fortran}{x = len - i};  \\
\noindent
3) \textbf{Inconsistent induction dimensions} occur when
an induction variable is used to specify more than one array dimension
on the RHS or multiple induction variables are used for the same
dimension on the RHS. These are common in matrix operations such as
LU-decomposition with assignments such as
\mintinline{fortran}{a(l) = a(l) - a(m) * b(l, m)}.

>>>>

We measured the frequency at which individual specifications involved
multiple occurrences of \term{*}
and \term{+}:
\begin{center}
\vspace{0.25em}
\setlength{\tabcolsep}{0.57em}
{\small{
\hspace{-1em}\begin{tabular}{c|cccccccc}
& 0 & 1 & 2 & 3 & 4 & 5 & 6  \\ \hline
\term{*} & \num{\overallmulOpszero} & \num{\overallmulOpsone} & \num{\overallmulOpstwo} & \num{\overallmulOpsthree} & \num{\overallmulOpsfour} &  & \num{\overallmulOpssix} \\
\term{+} & \num{\overallplusOpszero} & \num{\overallplusOpsone} & \num{\overallplusOpstwo}
\end{tabular}}}
\vspace{0.2em}
\end{center}

% \eg{}, roughly half the specifications did not involve $\term{*}$,
% a quarter use one $\term{*}$ and just under a quarter
% use two $\term{*}$ operators.

\subsection{Limitations}

There were various reasons why we did not infer
specifications on every looped array computation:
\begin{itemize}
\item \textbf{Non-subset induction variables} occur when the
induction variables on the RHS are not a subset of those in the LHS. These
cases are not stencils by our definition. The degenerate case of this
is to have only constant indices on the LHS. We see lots of examples
of this in loops as accumulators \eg{} computing the sum over an array;

\item \textbf{Derived induction variables} where an
index (\mintinline{fortran}{x}) is derived from an
induction variable (\mintinline{fortran}{i}) as in
\mintinline{fortran}{x = len - i};

\item \textbf{Inconsistent induction dimensions} occur when
an induction variable is used to specify more than one array dimension
on the RHS or multiple induction variables are used for the same
dimension on the RHS. These are common in matrix operations such as
LU-decomposition with assignments such as
\mintinline{fortran}{a(l) = a(l) - a(m) * b(l, m)}.
\end{itemize}
